Abstractions for Multi-Sorted Substitutions

### 2024-03-18 paper/paper.tex
Update.

  While intrinsic typing allows to unify definitions with their type
  preservation proofs, extrinsic typing allows to unify
  substitutions across different syntactic categories, as we have demonstrated.
  We believe this makes our framework particularly suited for polymorphic languages,
  where the downside of extrinsic typing is automated away, and the benefits
  of a unified substitution bears fruits.
  % Furthermore, extrinsic typing allows us
  % to avoid the ``subst-hell'', which typically appears in formalizations
  % of logical relations for polymorphic languages.
  % We believe this makes extrinsic typing more suitable for polymorphic languages:
  % with extrinsic typing, the definitions and lemmas for untyped
  % substitutions can be automated for virtually any object language,
  % whereas with intrinsic typing, it seems impossible to unify
  % substitutions across syntactic categories, because an intrinsically
  % typed multi-sorted syntax would require to index terms with terms,
  % which is the same problem that occurs with giving intrinsic types to a dependently typed language.

>>>>

  While intrinsic typing allows to unify definitions with their type
  preservation proofs, extrinsic typing allows to unify
  substitutions across different syntactic categories, as we have demonstrated.
  We believe this makes our framework particularly suited for polymorphic languages,
  where the downside of extrinsic typing is automated away, and where we have variables
  across multiple syntactic categories, so the benefits of a unified
  substitution bear fruits.
  % Furthermore, extrinsic typing allows us
  % to avoid the ``subst-hell'', which typically appears in formalizations
  % of logical relations for polymorphic languages.
  % We believe this makes extrinsic typing more suitable for polymorphic languages:
  % with extrinsic typing, the definitions and lemmas for untyped
  % substitutions can be automated for virtually any object language,
  % whereas with intrinsic typing, it seems impossible to unify
  % substitutions across syntactic categories, because an intrinsically
  % typed multi-sorted syntax would require to index terms with terms,
  % which is the same problem that occurs with giving intrinsic types to a dependently typed language.
